Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-31 WSSSPE3/report/WSSSPE3_review.tex
adding ref/cite for Gil talk

\item \textbf{Yolanda Gil, Chris Duffy, Chris Mattmann, Erin Robinson, and Karan
Venayagamoorthy: \textit{The Geoscience Paper of the Future Initiative: Training
Scientists in Best Practices of Software Sharing}}. Erin Robinson presented an
approach to overcome some hurdles in scientific publishing: disconnects among
experimental data, research software, and publications. A current effort in the
Geosciences is the ``Geoscience Paper of the Future,'' which includes four
elements. First, it forms a modern paper including text, data, and pointers to
supplementary materials. Second, it is reproducible, including data processing,
workflow, and visualization tools. Third, it is part of open science, which
includes being publicly available under open licenses, and providing meta-data.
Last but not least, it uses digital scholarship elements like persistent
identifiers for software, data, and authors, and it cites both data and
software. OntoSoft is a tool for helping with this effort, providing software stewardship
for the Geosciences. As part of this initiative, a special issue of a journal in
Geoscience areas is planned to include only Geoscience papers of the future,
with submissions open until the end of 2015. In addition, training sessions are
provided to geoscientists to learn best practices in software and data sharing,
provenance documentation, and scholarly publication.

>>>>

\item \textbf{Yolanda Gil, Chris Duffy, Chris Mattmann, Erin Robinson, and Karan
Venayagamoorthy: \textit{The Geoscience Paper of the Future Initiative: Training
Scientists in Best Practices of Software Sharing}}. Erin Robinson presented an
approach to overcome some hurdles in scientific publishing: disconnects among
experimental data, research software, and publications. A current effort in the
Geosciences is the ``Geoscience Paper of the Future,''\footnote{\url{http://www.ontosoft.org/gpf}} which includes four
elements~\cite{ESS2:ESS284}. First, it forms a modern paper including text, data, and pointers to
supplementary materials. Second, it is reproducible, including data processing,
workflow, and visualization tools. Third, it is part of open science, which
includes being publicly available under open licenses, and providing meta-data.
Last but not least, it uses digital scholarship elements like persistent
identifiers for software, data, and authors, and it cites both data and
software. OntoSoft is a tool for helping with this effort, providing software stewardship
for the Geosciences. As part of this initiative, a special issue of a journal in
Geoscience areas is planned to include only Geoscience papers of the future,
with submissions open until the end of 2015~\cite{GPFI}. In addition, training sessions are
provided to geoscientists to learn best practices in software and data sharing,
provenance documentation, and scholarly publication.
